---
title: "Pairwise Local Alignment of nucleotide sequences"
author: "Alessandro Gennari"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pairwise Local Alignment of nucleotide sequences}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(stringr)
library(pairwiseLocalAlignment)
```

## Introduction
In the comparison of two nucleotide sequences is fundamental the research of overlapping patterns. Smith-Waterman algorithm allow to perform pairwise loca alignment of two sequences in order to find patterns in common.

## Example

Performing Smith-Waterman algorithm means overlapping each nucleotide of the first sequence with each nucleotide of the second sequence and computing a score for each combination. All the scores are collected in aa matrix which allow to find the best local alignment with a 'trace back' procedure.
All those steps are performed by the smith_waterman function, which return a list of two elements collecting the aligned sub-sequences. 
This function require 3 numerical parameters which defines the cost of a match, mismatch or the insertion of a gap between nucleotides, and finally the two sequences

```{r}
seq1 <- 'CCTATACCTAATTTTCGGCGCATGAGCCGGAATGGTGGGTACCGCTCTAAGCCTCCTCATTC'
seq2 <- 'CATGAGCTGGAATAGTAGGTACCGCCCTAAGCCTCCTAATTCGAGCAGAGCTAGGCCAACCC'

smith_waterman(10, -10, -3, seq1, seq2)
```
